Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 paper.tex
Fix bibtex references

Here is a lemma that we will use, taken from \cite{quant-ph/0406180}.

@@

In \cite{1804.01082}, a verifiable scheme is proposed. In \cite{1708.02130}, a blind scheme is proposed. (TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.

@@

Here we describe the scheme between the classical client and an honest quantum server. We mostly follow the logic in \cite{1804.01082}. We first follow \cite{quant-ph/0406180} to reduce the problem to an instance of local Hamiltonian.

@@

We then follow \cite{0704.1287} in writing each terms of $H$ into only $Z$ and $X$ measurements...

@@

We then follow \cite{1804.01082}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure. The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{quant-ph/0406180}.

>>>>

Here is a lemma that we will use, taken from \cite{kempe_kitaev_regev_2006}.

@@

In \cite{mahadev_delegation}, a verifiable scheme is proposed. In \cite{mahadev_qfhe}, a blind scheme is proposed. (TODO just make this CPA or whatever it actually is...) We propose a verifiable scheme with long output which can also be made blind.

@@

Here we describe the scheme between the classical client and an honest quantum server. We mostly follow the logic in \cite{mahadev_delegation}. We first follow \cite{kempe_kitaev_regev_2006} to reduce the problem to an instance of local Hamiltonian.

@@

We then follow \cite{biamonte_love_2008} in writing each terms of $H$ into only $Z$ and $X$ measurements...

@@

We then follow \cite{mahadev_delegation}. That is, the server would commit copies of the ground state of the Hamiltonian for the classical client to measure. The client would check whether the computation is done correctly using a modified Hamiltonian from \cite{kempe_kitaev_regev_2006}.
